---
title: "Covid Cases in R"
output:
  html_document:
    df_print: paged
---
# Covid-19 Kaynaklı En Fazla Ölümün Olduğu 25 Ülke

```{r include=FALSE}

library(httr)
library(readxl)
library(RCurl) #Bir link çalışmazsa diğer linki çalıştıracak bir kod var burada.

# http://memosisland.blogspot.com/2012/03/check-url-existance-with-r.html

url2 <- paste("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv")
GET(url2, write_disk(tf<-tempfile(fileext = ".csv")))

df=read.csv((tf))
```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
covid_death_total <- sum(df$deaths)
covid_cases_total <- sum(df$cases)

covid_death <- aggregate(df$deaths, by=list(countriesAndTerritories=df$countryterritoryCode), FUN=sum)
covid_death_tr <- covid_death[186,2]

covid_cases <- aggregate(df$cases, by=list(countriesAndTerritories=df$countryterritoryCode), FUN=sum)
covid_cases_tr <- covid_cases[186,2]

covid_death_top <- aggregate(x = df$deaths,
          by = list(df$countriesAndTerritories),              
          FUN = sum) 

covid_death_top_25 <- covid_death_top[order(-covid_death_top$x),]

head(covid_death_top_25,n=25)

```
Dünya genelinde `r Sys.Date()` tarihine kadar Covid-19 tespit edilen vaka sayısı `r covid_cases_total` olmuştur. .

Dünya genelinde `r Sys.Date()` tarihine kadar Covid-19'dan ölen toplam kişi sayısı `r covid_death_total` olmuştur. 

Türkiye genelinde `r Sys.Date()` tarihine kadar Covid-19 tespit edilen vaka sayısı `r covid_cases_tr` olmuştur. 

Türkiye genelinde `r Sys.Date()` tarihine kadar Covid-19'dan ölen toplam kişi sayısı `r covid_death_tr` olmuştur. 

<!-- The features we have are: `r names(df)`. -->

# Türkiye İstatistikleri

```{r include=FALSE}
library(Hmisc)

# https://www.kaggle.com/gkhan496/covid19-in-turkey#covid_19_data_tr.csv

data <- read.csv("C:/Users/SATELLITE/Desktop/Covid_R/covid_19_data_tr.csv", stringsAsFactors = FALSE)

describe(data)
```

```{r include=FALSE}

library(lubridate)
data$Last_Update <- mdy(data$Last_Update)

# alternative
# data <- data %>%
# mutate(days = dmy(Last_Update))

```

#Türkiye için Toplam Ölüm / İyileşen Sayısı

```{r echo=FALSE}
library(directlabels)

base <- ggplot(data = data, ylim = c(0,200000), aes(x=Last_Update, 
                                y=Toplam_Kişi_Sayısı, group=1)) +
    geom_line(aes(y = Deaths), color="black",size=0.8, linetype="dashed") + 
  geom_line(aes(y = Recovered), color="steelblue",size=0.8, linetype = "twodash") +
 geom_text(aes(x = as.Date("2020-04-15"), y = 11500, label = "Toplam İyileşen", color = "Recovered")) + 
geom_text(aes(x = as.Date("2020-04-16"), y = 2500, label = "Toplam Ölüm", color = "Deaths"))
  
  base + scale_x_date(date_breaks = "4 days", date_labels = "%b %d")  
    
```

```{r echo=FALSE, message=FALSE}
library(dplyr)
library(DT)
edf <- df %>% group_by(countriesAndTerritories) %>% mutate(deathRate = sum(deaths)/sum(cases))

datatable(
edf[,c(1,5,6,7,11)], extensions = 'Buttons', options = list(
dom = 'Bfrtip',
buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
)
)

```

# Grafikler {.tabset}

## Grafik A 

```{r echo=FALSE}
library(ggplot2)

edf %>% filter(deaths > 50) %>%
group_by(countriesAndTerritories) %>%
summarise(Toplam_Olum = sum(deaths)) %>%
ggplot(aes(countriesAndTerritories)) +
geom_point(aes(y = Toplam_Olum, color = "red", size = Toplam_Olum)) +
coord_flip()
```

## Grafik B 

```{r echo=FALSE}
library(scales) # to access break formatting functions

edf %>% filter(cases > 1000) %>%
group_by(countriesAndTerritories) %>%
summarise(Toplam_Vaka = log2(sum(cases))) %>%

ggplot(aes(countriesAndTerritories)) +
geom_point(aes(y = Toplam_Vaka, color = "red", size = Toplam_Vaka)) +
coord_flip() 
```

# Dinamik Dünya Grafikleri

```{r include=FALSE, echo=FALSE, message=FALSE}
#Part1_CDCWebscraping.R

# install.packages( "rvest")
library(rvest)

# This is the URL at which the list of affected countries is given. Copy the url within quotes and paste this in web browser to see the page. 

# Updated on 19-03-2020: The url is changed from 
# URL <- "https://www.cdc.gov/coronavirus/2019-ncov/locations-confirmed-cases.html#map"
# to
URL <- "https://www.cdc.gov/coronavirus/2019-ncov/cases-updates/world-map.html"
# Actual Web Scraping the URL

# In this line we will read the url using 'read_html' function.

PAGE <- read_html(URL) %>%
  
# After reading the html we will extract the html potion by using the xpath from the original url. You can see video how I copied this xpath which is in quotes here. 

# UPDATE ON THIS LINE OF CODE (*Dated: 07-March-2020*): 
# The video contains the xpath to previous version of CDC website. Previously that `xpath` was `/html/body/div[6]/main/div[3]/div/div[3]/div/div/ul` which can be seen in the video and in above lines but after the CDC has updated the website along with the list of affected countries, We now have to change the xpath in our code too. The new xpath is now `/html/body/div[6]/main/div[3]/div/div[3]/div[2]` that is updated below as well:
# UPDATE (Dated: 25/03/2020)
# Now the xpath is again changed to "/html/body/div[7]/main/div[3]/div/div[3]/div[2]" so instead of previous one "/html/body/div[6]/main/div[3]/div/div[3]/div[2]" we will use new one. 
  
    html_nodes(xpath="/html/body/div[7]/main/div[3]/div/div[4]/div[2]") %>%
  
# Now the map function of purrr package will be used to get the 'li' node of html which actually contains all the names of the countries. 
  
    purrr::map(~html_nodes(.x, 'li') %>% 
                 
# After taking the list we will convert into text form. 
  
              html_text() %>% 
  
# gsub pattern extracts the things based on regex. Here I want to change the tabs (\\t), new lines (\\n) and returns (\\r) to nothing ('').  
  
              gsub(pattern = '\\t|\\r|\\n', replacement = ''))

# Now I am saving the list (PAGE[[1]]) to countries.

countries <- PAGE[[1]]

# Lets print this object. 

countries

# List of countries will be Converted to Dataframe. 

countries <- as.data.frame(matrix(unlist(countries),nrow=length(countries),byrow=TRUE))

# Now I want to change the name of column of dataframe to "Countries"

names(countries)[1] <- "Countries"

# Lets add a new column named as (Sr.No.) and add the sequence of numbers of series of numbers into it. 

Countriestable <- data.frame(Sr.No.=seq.int(nrow(countries)),countries)

# Lets print this dataframe.
# Total number of affected countries on date 07-03-2020 = 89

Countriestable


```


```{r include=FALSE, message=FALSE}
#Part2_PLottingCountriesUsingLeaflet.R

# install.packages("stringr")
# install.packages("maps")
# install.packages("ggplot2")
# install.packages("sf")
# install.packages("dplyr")
# install.packages("raster")
# install.packages("GADMTools")
# install.packages("rgeos")
# install.packages("leaflet")

library(stringr)
library(maps)
library(ggplot2)
library(sf)
library(dplyr)
library(raster)

# `map_data` is the function present in `ggplot2`. "Easily turn data from the maps package into a data frame suitable for plotting with `ggplot2`." We are using this to compare the list of countries told by CDC and those present in packcage.  

AllCountries <- map_data("world")

# Lets check the type of AllCountries which will be data.frame
class(AllCountries)

# Lets write AllCountries into a new txt file "NamesOfCountries.txt". It is only for learning how to write columns of a dataframe values as text in a text file. Here we are saving the values from the column `region` of `AllCountries` dataframe. 
write(AllCountries$region,"NamesOfCountries.txt")

# In the following command we will extract the values into an object `CountriesAvailable` for plotting. For that the column `region` of dataframe `AllCountries` will be grouped (`group_by()`). Later the `summarise()` function will summarise the countries/region and make a row for each.
CountriesAvailable<- AllCountries %>% group_by(region) %>% summarise()

# Now we will calculate the differences between the names of countries present in objects `Countriestable` and `CountriesAvailable`. This is due to the differences of names of countries present in real world and coded in packages like in map. For example, USA can be written as United States.  
setdiff(as.character(Countriestable$Countries), CountriesAvailable$region)

# So the countries given on website of CDC.gov is United States but we would require this as USA so that map can be plotted.This is because the name of country in package is USA. There are other countries as well including Macau, The Republic of Korea and United Kingdom which will be required to change as well. Here we are changing the values in Countries column of Countriestable (`Countriestable$Countries`) for USA, UK and South Korea only. Macau and Hong Kong will not be changed due to a reason discussed further. 

# Before
Countriestable$Countries

# Changes reqruied in the names of the countries
Countriestable$Countries <- recode(Countriestable$Countries, "United States" = "USA")
Countriestable$Countries <- recode(Countriestable$Countries, "United Kingdom" = "UK")
# Updated on 19-03-20: Change of Republic of Korea to South Korea
Countriestable$Countries <- recode(Countriestable$Countries, "Republic of Korea" = "South Korea")
#Update
Countriestable$Countries <- recode(Countriestable$Countries, "North Macedonia" = "Macedonia")
Countriestable$Countries <- recode(Countriestable$Countries, "Bosnia" = "Bosnia and Herzegovina")
Countriestable$Countries <- recode(Countriestable$Countries, "Holy See (Vatican City)" = "Vatican")
Countriestable$Countries <- recode(Countriestable$Countries, "Czechia" = "Czech Republic")
# Update Dated 12-03-2020
Countriestable$Countries <- recode(Countriestable$Countries, "Brunei Darussalam" = "Brunei")
#Updated on 19-03-2020
Countriestable$Countries <- recode(Countriestable$Countries, "Eswatini" = "Swaziland")
Countriestable$Countries <- recode(Countriestable$Countries, "Ivory Coast (Côte d’Ivoire)" = "Ivory Coast")
Countriestable$Countries <- recode(Countriestable$Countries, "Congo" = "Democratic Republic of the Congo")

# Deleted the combinations of countries and the duplicated values. Combinations will be added later on appended separately. 
#Updated on 19-03-2020
Countriestable<-Countriestable[!(Countriestable$Countries=="Antigua and Barbuda"),]
Countriestable<-Countriestable[!(Countriestable$Countries=="Democratic Republic of Congo"),]
Countriestable<-Countriestable[!(Countriestable$Countries=="Saint Vincent and the Grenadines"),]
Countriestable <- Countriestable[!(Countriestable$Countries=="Trinidad and Tobago"),]
#Updated on 19-03-2020
Country_Antigua <- data.frame(Sr.No.=nrow(Countriestable)+1,Countries="Antigua")
Countriestable <-  rbind(Countriestable, Country_Antigua)
Country_Barbuda <- data.frame(Sr.No.=nrow(Countriestable)+1,Countries="Barbuda")
Countriestable <-  rbind(Countriestable, Country_Barbuda)
# Added two new names and deleted their combination
#Updated on 19-03-2020
Country_SaintVincent <- data.frame(Sr.No.=nrow(Countriestable)+1,Countries="Saint Vincent")
Countriestable <-  rbind(Countriestable, Country_SaintVincent)
Country_Grenadines <- data.frame(Sr.No.=nrow(Countriestable)+1,Countries="Grenadines")
Countriestable <-  rbind(Countriestable, Country_Grenadines)
# Added two new names and deleted their combination above
#Updated on 19-03-2020
Country_Trinidad <- data.frame(Sr.No.=nrow(Countriestable)+1,Countries="Trinidad")
Countriestable <-  rbind(Countriestable, Country_Trinidad)
Country_Tobago <- data.frame(Sr.No.=nrow(Countriestable)+1,Countries="Tobago")
Countriestable <-  rbind(Countriestable, Country_Tobago)

# Updated on 25-03-2020
Countriestable$Countries <- recode(Countriestable$Countries, "Cabo Verde" = "Cape Verde")

# After Changes
Countriestable$Countries

# Ok now it is time to let you know that Why we left Hong Kong and Macau. This is because first the Macau is not present in the mapping package but is given on CDC website. So we want to map it by some other package which can map it. Moreover, we want Hong Kong to be mapped using the same package as well. So in summary we want to map the countries using two different ways. One is the `maps` package and other is `GADMTools`.   

library(GADMTools)
library(rgeos)

# Following command will download the simple map (level=0) of Hong Kong from gadm.org. You can see the list of countries at https://gadm.org/maps.html and download the realted maps from dropdown given at https://gadm.org/download_country_v3.html. 
HKMap <- getData('GADM', country='Hong Kong', level=0)
class(HKMap)
# Find a center point for Hong Kong map so that later we can add label in the center of the country upon mapping it. 
centerHK <- data.frame(gCentroid(HKMap, byid = TRUE))

# Similarly, map of makao(given at GADM.org) instead of macau (given at CDC.gov) can be seen at https://gadm.org/maps/MAC.html. 
MACMap <- getData('GADM', country='macao', level=0)
# Find a center point for Macao/u map
centerMAC <- data.frame(gCentroid(MACMap, byid = TRUE))

########## Updated for Gibraltar
GBMap <- getData('GADM', country='Gibraltar', level=0)
class(GBMap)
centerGB <- data.frame(gCentroid(GBMap, byid = TRUE))
centerGB

# Now we have data and maps related to all countries mentioned at CDC.gov which are affected with Coronavirus. We will map these countries using leaflet package. You can see my video about leaflet at https://www.youtube.com/watch?v=oxMOMpL_bys.

library(leaflet)

# Fist we will find the boundries of all the countries given in `Countriestable$Countries`. 
boundries <- maps::map("world", Countriestable$Countries, fill = TRUE, plot = FALSE)
# Lets check type of boundries object.
class(boundries)

# Finally plot all countries. Initiate leaflet()
Map_AffectedCountries <- leaflet() %>%

# Add providerTiles
addProviderTiles("OpenStreetMap.Mapnik") %>%

# Add polygons from boundries object 
addPolygons(data = boundries, group = "Countries", 
              color = "Blue", 
              weight = 2,
              smoothFactor = 0.2,
              popup = ~names,
              fillOpacity = 0.1,
              highlightOptions = highlightOptions(color = "black",
                                                  weight = 2, 
                                                  bringToFront = FALSE)) %>%

# Add polygon data for Hong Kong stored in object HKMap.  
addPolygons(data=HKMap, group = "id",
              color = "red", 
              weight = 2,
              smoothFactor = 0.2,
              popup = "Hong Kong",
              fillOpacity = 0.1,
              highlightOptions = highlightOptions(color = "black", 
                                                  weight = 2,
                                                  bringToFront = FALSE)) %>%
  
# Let's add the label only marker for the name of Hong Kong in center of that country
addLabelOnlyMarkers(data = centerHK, lng = ~x, lat = ~y, 
                    label = "Hong Kong", 
                    labelOptions = labelOptions(noHide = F, 
                                                textsize = "15px", 
                                                direction = 'top', 
                                                textOnly = TRUE))    %>%

# Let's add polygon data for Macao/u stored in object MACMap. 
addPolygons(data=MACMap, group = "id",
              color = "red", 
              weight = 2,
              smoothFactor = 0.2,
              popup = "Macau",
              fillOpacity = 0.1,
              label = "Macau",
              labelOptions = labelOptions(noHide = F, 
                                          textsize = "15px",
                                          direction = 'top'),
              highlightOptions = highlightOptions(color = "black", 
                                                  weight = 2,
                                                  bringToFront = FALSE))



# Generate the leaflet map
Map_AffectedCountries

########## Updated for Guadalupe 
boundryGuadalupe <- maps::map("world", "Mexico:Guadalupe Island", fill = TRUE, plot = FALSE)

Map_AffectedCountries <- Map_AffectedCountries %>%
  addProviderTiles("OpenStreetMap.Mapnik") %>%
  addPolygons(data = boundryGuadalupe, group = "Countries", 
              color = "red", 
              weight = 2,
              smoothFactor = 0.2,
              #popup = ~names,
              fillOpacity = 0.1,
              highlightOptions = highlightOptions(color = "black",
                                                  weight = 2,bringToFront = FALSE)) %>%
  ########## Updated for Gibraltar
  
  addPolygons(data=GBMap,group='id',
              color = "red", 
              weight = 2,
              smoothFactor = 0.2,
              popup = "Gibraltar",
              fillOpacity = 0.1,
              label = "Gibraltar",
              labelOptions = labelOptions(noHide = F, textsize = "15px",                                         direction = 'top'),
              highlightOptions = highlightOptions(color = "black", weight = 2,
                                                  bringToFront = F))
Map_AffectedCountries
```


```{r echo=FALSE, message=FALSE}
#Part3_PlottingValuesonLeaflet.R

#########################################                        
# Part 3
#########################################

# Install Libraries
# install.packages("readr")
# install.packages("knitr") 
# install.packages("RCurl")
# install.packages("htmlwidgets")
# install.packages("htmltools")

# Call Libraries
library(readr)
library(knitr) 
library(RCurl)
library(htmlwidgets)
library(htmltools)
#------------------------------------------
# Copy the raw path of CSVs
# Update (Dated: *25-03-2020*)
# The data files currently in use below are deprecated. The new files on the same github repo are changed. Following message can be seen on [https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series](https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series)
# *---DEPRICATED WARNING---
# The files below will no longer be updated. With the release of the new data structure, we are updating our time series tables to reflect these changes. Please reference time_series_covid19_confirmed_global.csv and time_series_covid19_deaths_global.csv for the latest time series data.*

Main <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series"
# Updated on 25-03-2020
# confirmed <-  file.path(Main,"time_series_19-covid-Confirmed.csv")
confirmed <-  file.path(Main,"time_series_covid19_confirmed_global.csv")
# 
confirmed
# Updated on 25-03-2020
# Deaths <- file.path(Main,"time_series_19-covid-Deaths.csv")
Deaths <- file.path(Main,"time_series_covid19_deaths_global.csv")
Deaths
# Updated on 25-03-2020
# The updated file on the recovered data is still awaited, for tutorial we are taking the deprecated file which will be updated later.
Recoverd<- file.path(Main,"time_series_covid19_recovered_global.csv")
Recoverd
ConfirmedData <- read.csv(confirmed)
DeathData <- read.csv(Deaths)
RecoveredData <-  read.csv(Recoverd)


#------------------------------------------
# DateColumn represents which column or date we are interested in for plotting. 
# Previous One
#DateColumn<- "X2.29.20"
# UPDATED on 19-03-2020 for getting the last column header of the ConfirmedData automatically to stay updated. Rest of the code will remain same. 
DateColumn <- colnames(ConfirmedData)[ncol(ConfirmedData)]
cleanDateColumn <- gsub('X','',DateColumn)
#------------------------------------------
# Different popups for Confirmed, Deaths and Recovered Cases. These popups will popup when we click the circles.

popupConfirmed <- paste("
                        <strong>County: </strong>", 
                        ConfirmedData$Country.Region, 
                        "<br><strong>Province/State: </strong>", 
                        ConfirmedData$Province.State, 
                        "<br><strong>Confirmed: </strong>", 
                        ConfirmedData[,DateColumn]
                        )

popupdeath <- paste("
                    <strong>County: </strong>", 
                    DeathData$Country.Region, 
                    "<br><strong>Province/State: </strong>", 
                    DeathData$Province.State, 
                    "<br><strong>Deaths: </strong>", 
                    DeathData[,DateColumn] 
                    )

popupRecovered <- paste("
                        <strong>County: </strong>", 
                        RecoveredData$Country.Region, 
                        "<br><strong>Province/State: </strong>", 
                        RecoveredData$Province.State, 
                        "<br><strong>Recovered: </strong>", 
                        RecoveredData[,DateColumn]
                        )

#------------------------------------------
# Different Color Pallets for Confirmed, Deaths and Recovered Cases

palConfirmed <- colorBin(palette = "GnBu", domain = ConfirmedData[,DateColumn] , bins = 3 , reverse = FALSE)

paldeath     <- colorBin(palette = "OrRd", domain = DeathData[,DateColumn]     , bins = 3 , reverse = FALSE)

palrecovered <- colorBin(palette = "BuGn", domain = RecoveredData[,DateColumn] , bins = 3 ,  reverse = FALSE)

#------------------------------------------
# We want to add text on the map which represent Title, Subtitle and number of cases. For this we will use CSS styles and HTML. 

title <- tags$style(HTML("
                         .map-title {
                         font-family: 'Cool Linked Font', fantasy; 
                         transform: translate(-10%,20%); 
                         position: fixed !important; 
                         left: 10%; 
                         text-align: left; 
                         padding-left: 10px; 
                         padding-right: 10px; 
                         background: rgba(255,255,255,0.75); 
                         font-weight: bold; 
                         font-size: 25px}")
                        )


subtitle <- tags$style(HTML("
                            .map-subtitle {
                            transform: translate(-10%,150%);
                            position: fixed !important;
                            left: 10%;
                            text-align: left;
                            padding-left: 10px;
                            padding-right: 10px;
                            font-size: 18px}")
                            )

CasesLabel<- tags$style(HTML("
                             .cases-label{
                             position: absolute; 
                             bottom: 8px; 
                             left: 16px; 
                             font-size: 18px}")
                            )
#------------------------------------------
# Here we will write what we want to show as Title, Subtitle and Cases in HTML format over Map. 


leaflettitle <- tags$div(title, HTML("Status of COVID-19"))  

leafletsubtitle <- tags$div(subtitle, HTML("World Map"))  

CasesLabelonMap <- tags$div(CasesLabel, HTML(paste(
  "<strong>Date: </strong>", 
  cleanDateColumn, 
  "<strong>Confirmed: </strong>",
  sum(as.numeric(ConfirmedData[,DateColumn])), 
  "<strong>Deaths: </strong>",
  sum(as.numeric(DeathData[,DateColumn])),
  "<strong>Recovered: </strong>",
  sum(as.numeric(RecoveredData[,DateColumn]))))
                          )
CasesLabelonMap
#------------------------------------------
# Now we will add the information back into the leaflet map. For this we will use the object of `Map_AffectedCountries` which was used to make the map in previous part. 

Mapwithvalues <- Map_AffectedCountries %>% 
    
#------------------
# In the following code we will plot Confirmed cases and add the legend for it along with the control to show or hide this data. 

addCircleMarkers(data= ConfirmedData, 
                 lng = ~Long, 
                 lat = ~Lat, 
                 radius = ~log(ConfirmedData[,DateColumn])*5, 
                 stroke = FALSE, 
                 fillOpacity = 1, 
                 popup = popupConfirmed, 
                 color = ~palConfirmed(ConfirmedData[,DateColumn]), 
                 group = "Circles(Confirmed)") %>%

  
addLabelOnlyMarkers(data= ConfirmedData, 
                      lng = ~Long, 
                      lat = ~Lat, 
                      label  = ~as.character(ConfirmedData[,DateColumn]), 
                      group="Values(Confirmed)", 
                      labelOptions = labelOptions(noHide = T, 
                                                  direction = 'center', 
                                                  textOnly = T, 
                                                  style=list('color'='blue', 
                                                             'font-family'= 'sans',
                                                             'font-style'= 'bold', 
                                                             'font-size' = '20px', 
                                                             'border-color' = 'rgba(0,0,0,0.5)'))) %>%
  
addLegend("bottomright", 
          pal = palConfirmed, 
          values = ConfirmedData[,DateColumn], 
          title = "Confirmed", 
          opacity = 1) %>%
  

#------------------
# In the following code we will plot Recovered cases and add the legend for it along with the control to show or hide this data.

addCircleMarkers(data= RecoveredData, 
                 lng = ~Long, 
                 lat = ~Lat, 
                 radius = ~log(X2.27.20)*5, 
                 stroke = FALSE, 
                 fillOpacity = 1, 
                 popup = popupRecovered, 
                 color = ~palrecovered(RecoveredData$X2.27.20), 
                 group = "Circles(Recovered)") %>%

  
addLabelOnlyMarkers(data= RecoveredData, 
                    lng = ~Long, 
                    lat = ~Lat, 
                    label  = ~as.character(RecoveredData[,DateColumn]), 
                    group="Values(Recovered)", 
                    labelOptions = labelOptions(noHide = T, 
                                                direction = 'center', 
                                                textOnly = T, 
                                                style=list('color'='green', 
                                                           'font-family'= 'sans', 
                                                           'font-style'= 'bold', 
                                                           'font-size' = '20px',
                                                           'border-color' = 'rgba(0,0,0,0.5)'))) %>%
  
addLegend("bottomright", 
          pal = palrecovered, 
          values = RecoveredData[,DateColumn], 
          title = "Recovered", 
          opacity = 1) %>%
  
#------------------
# In the following code we will plot Deaths and add the legend for it along with the control to show or hide this data.

addCircleMarkers(data= DeathData, 
                 lng = ~Long, 
                 lat = ~Lat, 
                 radius = ~log(DeathData[,DateColumn])*5, 
                 stroke = FALSE, 
                 fillOpacity = 1, 
                 popup = popupdeath, 
                 color = ~paldeath(DeathData[,DateColumn]), 
                 group = "Circles(Death)") %>%
  
addLabelOnlyMarkers(data= DeathData, 
                      lng = ~Long, 
                      lat = ~Lat, 
                      label  = ~as.character(DeathData[,DateColumn]), 
                      group="Values(Death)", 
                      labelOptions = labelOptions(noHide = T, 
                                                  direction = 'center', 
                                                  textOnly = T, 
                                                  style=list('color'='red', 
                                                             'font-family'= 'sans', 
                                                             'font-style'= 'bold',
                                                             'font-size' = '20px',
                                                             'border-color' = 'rgba(0,0,0,0.5)'))) %>%
  
  
addLegend("bottomright", 
          pal=paldeath, 
          values=DeathData[,DateColumn], 
          title = "Deaths", 
          opacity = 1) %>%
  
#------------------
# In the following code, we are actually showing the check boxes for showing or hiding the circles and values for cases. 

addLayersControl(overlayGroups = c("Circles(Confirmed)","Values(Confirmed)" ,"Circles(Recovered)","Values(Recovered)", "Circles(Death)","Values(Death)"), options = layersControlOptions(collapsed = FALSE)) %>%

  
#------------------
# In the following code, we will add title, subtitle, and number of cases over the map.

addControl(leaflettitle, position = "topleft", className="map-title") %>%
    
addControl(leafletsubtitle, position = "topleft", className="map-subtitle") %>%
  
addControl(CasesLabelonMap, position = "bottomleft", className="cases-label")

#------------------------------------------
# Show the map 
Mapwithvalues

#------------------------------------------
# Save this map as html file for presenting it later
saveWidget(Mapwithvalues, file="map1.html", selfcontained=FALSE)
```

# Dinamik Türkiye Grafiği

```{r echo=FALSE, message=FALSE}

#Part4_Timeseries.R

# Install Libraries
# install.packages("tidyverse")
# install.packages("plotly")
# install.packages("cowplot")
# install.packages("grid")
# Call Libraries
library(tidyverse)
library(plotly)
library(cowplot)
library(grid)

# Main Path for getting the data in the form of CSVs
Main <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series"
# Update (Dated: *25-03-2020*)
# The data files currently in use below are deprecated. The new files on the same github repo are changed. Following message can be seen on [https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series](https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series)
# *---DEPRICATED WARNING---
#  The files below will no longer be updated. With the release of the new data structure, we are updating our time series tables to reflect these changes. Please reference time_series_covid19_confirmed_global.csv and time_series_covid19_deaths_global.csv for the latest time series data.*

# We are saving the links to each CSVs in separate objects
# Updated on 25-03-2020
# confirmed <-  file.path(Main,"time_series_19-covid-Confirmed.csv")
confirmed_Path <-  file.path(Main,"time_series_covid19_confirmed_global.csv")
# 
confirmed
# Updated on 25-03-2020
# Deaths <- file.path(Main,"time_series_19-covid-Deaths.csv")
Deaths_Path <- file.path(Main,"time_series_covid19_deaths_global.csv")
Deaths
# Updated on 25-03-2020
# The updated file on the recovered data is still awaited, for tutorial we are taking the deprecated file which will be updated later.
# Updated on 12-04-2020
# The csv is updated from  `time_series_19-covid-Recovered.csv` to `time_series_covid19_recovered_global.csv`
Recoverd_Path <- file.path(Main,"time_series_covid19_recovered_global.csv")
Recoverd

# Now, we are reading the data stored in each link
ConfirmedData <- read.csv(confirmed_Path,stringsAsFactors = FALSE)
DeathData     <- read.csv(Deaths_Path,stringsAsFactors = FALSE)
RecoveredData <- read.csv(Recoverd_Path,stringsAsFactors = FALSE)

# Based on the region, the information will be fetched and prepared
Region <- "Turkey"

# This function is important for making the data to be used in animations generated by Plotly
accumulate_by <- function(dat, var) {
  var <- lazyeval::f_eval(var, dat) 
  lvls <- plotly:::getLevels(var) 
  dats <- lapply(seq_along(lvls), 
                 function(x) {
                   cbind.data.frame(dat[var %in% lvls[seq(1, x)], ],
                                    frame = lvls[[x]])}) 
  dplyr::bind_rows(dats)}

# This DataClean function is requried to change the wide table into long table and then filtering the data according to region mentioned above
DataClean <- function(data, region, CaseType) {
  CleanedData <- data %>% 
    pivot_longer(cols = starts_with("X"), 
                 names_to = "Date", 
                 names_prefix = "X", 
                 names_ptypes = list(week = integer()), 
                 values_to = CaseType, 
                 values_drop_na = TRUE)   %>% 
    mutate(Province.State = ifelse(Province.State %in% "", Country.Region, Province.State)) %>% 
    mutate(Date = as.Date(Date, "%m.%d.%y")) %>% 
    filter(Province.State == region) %>% 
    arrange(Date) %>% 
    mutate(ID = row_number()) 
  return(CleanedData)
  }

# Now we are cleaning data for each case
ConData <- DataClean(ConfirmedData,Region,"Confirmed") 

RecData <- DataClean(RecoveredData,Region,"Recovered")  

DeData <-DataClean(DeathData,Region,"Deaths")          


# In this code we are going to merge the cleaned data according to the ID column
AllData <- list(ConData, RecData, DeData)              %>% reduce(left_join, by = "ID")


# In this code, we are generating the frames for animations.
frames <- AllData %>% accumulate_by(~ID)


# METHOD 1 (Animated graphs using ggplotly() after making ggplot()): Now we will generate a combined plot by ggplot for all cases and their time series in region mentioned above

plot <- ggplot(data=frames,aes(x=Date, frame = frame)) + 
  geom_line(aes(y=Confirmed, colour="Confirmed"),size=1) + 
  geom_line(aes(y= Recovered, colour = "Recovered"),size=1) + 
  geom_line(aes(y= Deaths, colour = "Deaths"),size=1) + 
  labs(colour="Cases") + 
  scale_color_manual(values=c('#0751B8','#B82607', '#0BB807')) + 
  theme_bw()+ 
  theme(legend.box.background = element_rect(), 
        legend.box.margin = margin(6, 6, 6, 6)) + 
  labs(title = paste("Cases Over the Period of Time Since First Report in",Region), 
       subtitle = "World Map", 
       x = "Date",
       y="Cases") 


# Plot the plot
plot

# In fig1, we are going to produce the animations by using ggplotly()
fig1 <- ggplotly(plot) %>% 
  animation_opts(frame = 100, 
                 transition = 0, 
                 redraw = FALSE) %>% 
  animation_slider(currentvalue = list(prefix = "Day ")) 


# Plot the animated fig1
fig1

# In this code, we are going to generate the static plot for conifrmed cases only by using ggplot()
subplot1 <- ggplot(data=frames,aes(x=Date, frame = frame)) + 
  geom_line(aes(y=Confirmed, colour="Confirmed"), color = "#0751B8",size=1) +  
  labs(colour="Cases") + 
  theme_bw()

# Plot subplot1
subplot1

# In this code, we are going to generate the static plot for Receovered cases only by using ggplot()
subplot2 <- ggplot(data=frames,aes(x=Date, frame = frame)) + 
  geom_line(aes(y=Recovered, colour="Recovered"), color = "#0BB807",size=1) + 
  labs(colour="Cases") + 
  theme_bw()

# plot subplot2
subplot2

# In this code, we are going to generate the static plot for Deaths only by using ggplot()
subplot3 <- ggplot(data=frames,aes(x=Date, frame = frame)) +  
  geom_line(aes(y=Deaths, colour="Deaths"), color = "#B82607",size=1) +  
  labs(colour="Cases") +  
  theme_cowplot(12)

# plot subplot3
subplot3

# In this code, we will generate a new page for grid alignment of all three subplot1-3.
grid.newpage()
grid.draw(rbind(ggplotGrob(subplot1), 
                ggplotGrob(subplot2),
                ggplotGrob(subplot3), 
                size = "last"))

# This is another way to subplot three subplots 1-3.
cowplot::plot_grid(subplot1,subplot2,subplot3, labels = c('A', 'B','C'), label_size = 12, align = "v", ncol = 1)


# METHOD 2 (Animated graphs using plot_ly() without making ggplot()): Now We will use plot_ly() function to make an animated graph.

fig2 <- plot_ly() %>%  
  
  # We are going to add the information of Confirmed cases by using add_trace()
  add_trace(data=frames, 
            x = ~Date, 
            y = ~Confirmed, 
            name= 'Confirmed', 
            frame = ~frame,  
            type = 'scatter', 
            mode = 'lines+markers', 
            marker = list(size = 10, 
                          color = 'rgba(51, 153, 255, .5)', 
                          line = list(color = 'rgba(0, 38, 77, .8)', width = 2)), 
            line = list(color = 'rgba(0, 38, 77, .8)', 
                        width = 2)) %>% 
  
  # We are going to add the information of Recovered cases by using add_trace()
  add_trace(data=frames, 
            x = ~Date, 
            y = ~Recovered, 
            name='Recovered', 
            frame = ~frame,  
            type = 'scatter', 
            mode = 'lines+markers', 
            marker = list(size = 10, 
                          color = 'rgba(153, 255, 153, .8)', 
                          line = list(color = 'rgba(0, 179, 0, .8)', width = 2)), 
            line = list(color = 'rgba(0, 179, 0, .8)', 
                        width = 2)) %>% 
  
  # We are going to add the information of Deaths by using add_trace()
  add_trace(data=frames, 
            x = ~Date, 
            y = ~Deaths, 
            name='Deaths', 
            frame = ~frame, 
            type = 'scatter', 
            mode = 'lines+markers',
            marker = list(size = 10, 
                          color = 'rgba(255, 102, 102, .5)', 
                          line = list(color = 'rgba(152, 0, 0, .8)', width = 2)), 
            line = list(color = 'rgba(152, 0, 0, 1)', 
                        width = 2)) %>% 
  # Formating the layout of the graph
  layout(legend=list(x = 100, y = 0.5, yanchor="top"), 
         title = list(text=paste("<b> Cases Over the Period of Time in",Region, "Since First Report </b>"), 
                      size = 10), 
         xaxis=list(autoscale=FALSE,
                    range = c(head(frames$Date, n=1),tail(frames$Date, n=1)+2),
                    title = "<b> Days </b>"), 
         yaxis=list(title = "<b> Cases </b>")) %>%
  
  # Animation options
  animation_opts(10, easing = "elastic", redraw = TRUE)

# Plot the fig2
fig2

fig3 <- plot_ly() %>%  
  
  # We are going to add the information of Confirmed cases by using add_trace()
  add_trace(data=AllData, 
            x = ~Date, 
            y = ~Confirmed, 
            name= 'Confirmed', 
            type = 'scatter', 
            mode = 'lines+markers', 
            marker = list(size = 10, 
                          color = 'rgba(51, 153, 255, .5)', 
                          line = list(color = 'rgba(0, 38, 77, .8)', width = 2)), 
            line = list(color = 'rgba(0, 38, 77, .8)', 
                        width = 2)) %>% 
  
  # We are going to add the information of Recovered cases by using add_trace()
  add_trace(data=AllData, 
            x = ~Date, 
            y = ~Recovered, 
            name='Recovered', 
            type = 'scatter', 
            mode = 'lines+markers', 
            marker = list(size = 10, 
                          color = 'rgba(153, 255, 153, .8)', 
                          line = list(color = 'rgba(0, 179, 0, .8)', width = 2)), 
            line = list(color = 'rgba(0, 179, 0, .8)', 
                        width = 2)) %>% 
  
  # We are going to add the information of Deaths by using add_trace()
  add_trace(data=AllData, 
            x = ~Date, 
            y = ~Deaths, 
            name='Deaths', 
            type = 'scatter', 
            mode = 'lines+markers',
            marker = list(size = 10, 
                          color = 'rgba(255, 102, 102, .5)', 
                          line = list(color = 'rgba(152, 0, 0, .8)', width = 2)), 
            line = list(color = 'rgba(152, 0, 0, 1)', 
                        width = 2)) %>% 
  # Formating the layout of the graph
  layout(legend=list(x = 100, y = 0.5, yanchor="top"), 
         title = list(text=paste("<b> Cases Over the Period of Time in",Region, "Since First Report </b>"), 
                      size = 10), 
         xaxis=list(autoscale=FALSE,
                    range = c(head(frames$Date, n=1),tail(frames$Date, n=1)+2),
                    title = "<b> Days </b>"), 
         yaxis=list(title = "<b> Cases </b>"))
# Now If you want to generate three separate graphs by using plot_ly() function. First, subplotly1 represents the graph for confirmed cases. 

fig3

subplotly1 <-  plot_ly(AllData, 
                       x = ~Date, 
                       y = ~Confirmed,
                       name='Confirmed', 
                       type = 'scatter', 
                       mode = 'lines+markers',
                       marker = list(size = 10, 
                                     color = 'rgba(51, 153, 255, .5)', 
                                     line = list(color = 'rgba(0, 38, 77, .8)', width = 2)), 
                       line = list(color = 'rgba(0, 38, 77, .8)', 
                                   width = 2))
#plot Subplotly1
subplotly1

# Second, subplotly2 represents the graph for Recovered cases
subplotly2 <-  plot_ly(AllData, 
                       x = ~Date, 
                       y = ~Recovered,
                       name='Recovered', 
                       type = 'scatter', 
                       mode = 'lines+markers', 
                       marker = list(size = 10, 
                                     color = 'rgba(153, 255, 153, .8)', 
                                     line = list(color = 'rgba(0, 179, 0, .8)', width = 2)), 
                       line = list(color = 'rgba(0, 179, 0, .8)', 
                                   width = 2))

#plot subplotly2
subplotly2

# Third, subplotly3 represents the graph for confirmed cases
subplotly3 <- plot_ly(AllData, 
                      x = ~Date, 
                      y = ~Deaths,
                      name='Deaths',
                      type = 'scatter', 
                      mode = 'lines+markers',
                      marker = list(size = 10, 
                                    color = 'rgba(255, 102, 102, .5)', 
                                    line = list(color = 'rgba(152, 0, 0, .8)', width = 2)), 
                      line = list(color = 'rgba(152, 0, 0, 1)', 
                                  width = 2))

# plot subplotly3
subplotly3

# Now, if you want to make three subplotly1-3 horizontally 
figsubplotly <- subplot(subplotly1, subplotly2, subplotly3)

# plot figsubplotly
figsubplotly

# and if you want to change them vertically 
figsubplotlyrows <- subplot(subplotly1, subplotly2, subplotly3, nrows= 3, shareX = TRUE)

# plot figsubplotlyrows
figsubplotlyrows

```

